Cudele: A File System with Programmable Consistency and Durability

### 2017-03-22 paper/sections/3_posix_overheads.tex
paper: submit abstract and touch up intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: popperize graphs and fix links
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\section{POSIX Overheads}

@@

\subsection{Fault Tolerance}
\label{sec:fault-tolerance}
\begin{figure*}[tb] \centering
\includegraphics[width=1\textwidth]{./figures/journal.png} 
\caption{CephFS uses a journal to stage updates and tracks dirty metadata in
the collective memory of the MDSs. Each MDS maintains its own journal, which is
broken up into 4MB segments. These segments are pushed into RADOS and deleted
when that particular segment is trimmed from the end of the log. In addition to
journal segments, RADOS also stores per-directory objects. \label{fig:journal}}
\end{figure*}

\begin{figure*}[tb]%h
\centering
\includegraphics[width=180mm]{figures/throughput-journal.png}
\caption{Performance improves with larger journal segments because the metadata
server spends less time flushing the journal }\label{fig:throughput-journal}
\end{figure*}

@@

\begin{figure*}[tb]%h
\centering
\includegraphics[width=180mm]{figures/throughput-cache-journal.png}
\caption{Journalling metadata updates has a bigger overhead than maintaining
the inode cache. For create-heavy workloads the inode cache offers no
performance benefits. }\label{fig:throughput-cache-journal}
\end{figure*}

\begin{figure*}[tb]%h
\centering
\includegraphics[width=180mm]{figures/inode-cache.png}
\caption{The inode cache improves metadata read performance but for our
create-heavy workload it is only an overhead. Most of the time maintaining the
cache is spent evicting and adding inodes.}\label{fig:inode-cache}
\end{figure*}

@@

\begin{figure*}[tb]%h
\centering
\includegraphics[width=180mm]{figures/throughput-droplease.png}
\caption{When a client create stream is ``isolated" then lookups resolve
locally but when a second client ``interferes" by creating in the same directory,
the directory inode capability is revoked forcing all clients to centralize
lookups at the metadata server.  \label{fig:throughput-droplease}}
\end{figure*}

@@

\subsection{Consistency Overhead}
\begin{figure*}[tb]
\centering
\includegraphics[width=180mm]{figures/exp0-underloaded.png}
\caption{An underloaded metadata server adaquately services conflicting
clients; the create speeds are similar while the interferring operations are
limited by the cost of RPCs.}\label{fig:exp0-underloaded}
\end{figure*}

\begin{figure*}[tb]
\centering
\includegraphics[width=180mm]{figures/runtime-consistency-scale.png}
\caption{Scaling clients shows increased variability when another client
interferes; zooming in on runs with 7 clients we see that different types of
interferring operations have different effects on performance variability and
predictability.  }\label{fig:runtime-consistency-scale}
\end{figure*}

>>>>

\section{POSIX Overheads}
\label{sec:posix-overheads}

@@

\subsection{Fault Tolerance}
\label{sec:fault-tolerance}

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-journal.png}
      \caption{}
      \label{fig:phy-design}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/behavior-journal.png}
      \caption{}
      \label{fig:batching}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-cache.png}
      \caption{}
      \label{fig:batching-outlier}
  \end{subfigure}
  \caption{(a) relative performance differences are different after storage
  software upgrade. (b) total throughput with and without batching. (c)
  identifying and handling an outlier maintains the benefits
  of batching without the performance degradation of unnecessarily large I/O
  requests.}
\end{figure*}

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./graphs/behavior-cache.png} 
\caption{The inode cache improves metadata read performance but for our
create-heavy workload it is only an overhead. Most of the time maintaining the
cache is spent evicting and adding inodes.}\label{fig:inode-cache}
\end{figure}

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./figures/journal.png} 
\caption{CephFS uses a journal to stage updates and tracks dirty metadata in
the collective memory of the MDSs. Each MDS maintains its own journal, which is
broken up into 4MB segments. These segments are pushed into RADOS and deleted
when that particular segment is trimmed from the end of the log. In addition to
journal segments, RADOS also stores per-directory objects. \label{fig:journal}}
\end{figure}

%\begin{figure*}[tb]%h
%\centering
%\includegraphics[width=180mm]{figures/throughput-journal.png}
%\caption{Performance improves with larger journal segments because the metadata
%server spends less time flushing the journal }\label{fig:throughput-journal}
%\end{figure*}

@@

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/behavior-interfere.png}
      \caption{}
      \label{fig:phy-design}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere.png}
      \caption{}
      \label{fig:batching}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-interfere-types.png}
      \caption{}
      \label{fig:batching-outlier}
  \end{subfigure}
  \caption{When a client create stream is ``isolated" then lookups resolve
  locally but when a second client ``interferes" by creating in the same
  directory, the directory inode capability is revoked forcing all clients to
  centralize lookups at the metadata server.  An underloaded metadata server
  adaquately services conflicting clients; the create speeds are similar while
  the interferring operations are limited by the cost of RPCs.  Scaling clients
  shows increased variability when another client interferes; zooming in on runs
  with 7 clients we see that different types of interferring operations have
  different effects on performance variability and predictability.
  \label{fig:throughput-droplease}}
\end{figure*}

@@

\subsection{Consistency Overhead}

### 2017-03-22 paper/sections/6_results.tex
paper: submit abstract and touch up intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: popperize graphs and fix links
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\section{Results}
\subsection{Microbenchmarks}
\begin{figure*}[tb]
\centering
\includegraphics[width=180mm]{figures/results-microbenchmark.png}
\caption{Here's a graph.}
\end{figure*}

\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{figures/results-files.png}
\caption{Here's a graph.}
\end{figure}

\subsubsection{Per phase latencies}
\begin{figure}[tb]
\centering
\includegraphics[width=90mm]{figures/global-v-decoupled.png}
\caption{Compared to the \texttt{create} phase, saving and persisting
updates (\texttt{create+save} and \texttt{create+save+persist}) experience only
a 4.79\(\times\) and 8.66\(\times\) slowdown, in the worst case for 100K files.
In contrast, maintaining \texttt{global} consistency is 905.70\(\times\)
slower.  The disadvantage of decoupling the namespace is the merge phase where
updates are applied to the metadata store (\texttt{create+apply}, resulting in a
905.70\(\times\) slowdown for 100K files.}\label{fig:global-v-decoupled}
\end{figure}

@@

\subsection{Journaling Overhead}

Journal to RADOS
Turn off journaling (large segment)
Journal to in-memory OSD

>>>>

\section{Evaluation}
\label{sec:evaluation}

\subsection{Microbenchmarks}
%\begin{figure*}[tb]
%\centering
%\includegraphics[width=180mm]{graphs/slowdown.png}
%\caption{Compared to the \texttt{create} phase, saving and persisting
%updates (\texttt{create+save} and \texttt{create+save+persist}) experience only
%a 4.79\(\times\) and 8.66\(\times\) slowdown, in the worst case for 100K files.
%In contrast, maintaining \texttt{global} consistency is 905.70\(\times\)
%slower.  The disadvantage of decoupling the namespace is the merge phase where
%updates are applied to the metadata store (\texttt{create+apply}, resulting in a
%905.70\(\times\) slowdown for 100K files.}\label{fig:global-v-decoupled}
%\end{figure*}

\begin{figure}[tb]
\centering
\includegraphics[width=75mm]{graphs/slowdown-mechanisms.png}
\caption{}
\end{figure}
\begin{figure}[tb]
\centering
\includegraphics[width=75mm]{graphs/slowdown-related-work.png}
\caption{}
\end{figure}
\begin{figure}[tb]
\centering
\includegraphics[width=75mm]{graphs/slowdown-strong-v-eventual.png}
\caption{}
\end{figure}

\subsubsection{Per phase latencies}

@@

\subsection{Isolation from EBUSY}
\subsection{Isolation from Global Writes, Cost of Overwrites}
\subsection{Partial Directory Listings}
